FTLR proof cases

### 2018-06-27 fully-abstract-comp/ftlr-proof-cases.tex
Simplify xReadCond (thanks to the padding) and prove some results about splicing.

\begin{lemma}[Capability splicing retains safety for normal capabilities]
  \label{lem:splitting-safety-normal}
  If
  \begin{itemize}
  \item $\npair{(c_1,c_1)} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_2,c_2)} \in \lrvg{\trust}(W_2)$
  \item $c_1 = ((\perm,\lin),\baddr,n,\aaddr)$
  \item $c_2 = ((\perm,\lin),n,\eaddr,\aaddr)$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $b \le n \le e$
  \item $c_1' = \linCons{c_1}$
  \item $c_2' = \linCons{c_2}$
  \end{itemize}
  then there exist $W_1',W_2',W_3'$ such that
  \begin{itemize}
  \item $W_1 \oplus W_2 = W_1' \oplus W_2' \oplus W_3'$
  \item $\npair{(c,c)} \in \lrvg{\trust}(W_3')$
  \item $\npair{(c_1',c_1')} \in \lrvg{\trust}(W_1')$
  \item $\npair{(c_2',c_2')} \in \lrvg{\trust}(W_2')$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\begin{lemma}
  \label{lem:ftlr-internal-lemma}
  If
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $[b,e] \mathrel{\#} \ta$ and $\npair{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
  \item $\Phi_S(\pcreg) = \Phi_T(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$
  \item $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$
  \item $\memSat{\Phi_S.\mem,\Phi_S.\stk,\Phi_S.\ms_\stk,\Phi_T.\mem}{W_M}$
  \item $W_\pcreg \oplus W_R \oplus W_M$ is defined.
  \item Theorem~\ref{thm:ftlr} holds for all $n' < n$.
  \end{itemize}
  Then
  \[
    \npair{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  In the following we will use the following: $\reg_S = \Phi_S.\reg$, $\reg_T = \Phi_T.\reg$, $\ms_S = \Phi_S.\mem$, $\ms_\stk = \Phi_S.\ms_\stk$, and $\stk = \Phi_S.\stk$.

@@

  In case \ref{case:ftlr:failed}, both executions go to $\failed$.
  In this case, the result follows vacuously by definition of $\lrol$ and $\lror$.
  \\\\
  In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
  steps, so both directions of $\lro$ are trivially satisfied.
  \\\\
  In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to conclude
  \[
    \npair[n-1]{(\Phi_S',\Phi_T')} \in \lro
  \]
  from the following facts:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
    This follows from the corresponding assumption of this lemma and the fact that $\Phi_S \nstep[1]{\gc} \Phi_S'$ and Lemma~\ref{lem:ec-reasonable-antired}, \ref{lem:ec-reasonable-downwards-closed}, and \ref{lem:downwards-closed}.
  \item $\Phi_S'(\pcreg) = \Phi_T'(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$:
    Follows from the definition of $\updPcAddr{}$ and the assumptions of this case.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item $\npair[n-1]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}, the definition of $\lrr$ and the fact that integers are always in $\lrvg{\trust}$ by definition.
  \item $\memSat[n-1]{\Phi_S.\mem,\Phi_S.\ms_\stk,\Phi_S.\stk,\Phi_T.\mem}{W_M}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item Theorem~\ref{thm:ftlr} holds for all $n'' < n-1$:
    follows from the corresponding assumption of this lemma, since $n - 1 < n$.
  \end{itemize}

@@

  It remains to show \ref{case:ftlr:scall:world}-\ref{case:ftlr:scall:mem}, but first we note that we can deduce the following: From the assumption $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ we get $R \subseteq \addressable{\normal, \pwheap}$ and $\exists M : S \fun \powerset{\MemSeg}$ such that $\biguplus_{r\in S} \dom(M(r)) \supseteq [\baddr,\eaddr]$ and $\forall r \in S \ldotp \pwheap(r) \nequal \codereg{\sigrets',\_,M(r),\gc}$.
  Further by $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, we know that for one $r \in S$ there is a $\mscode' \subseteq \mscode$, call this $r$ for $r_{\mscode'}$,\footnote{Follows from $H^\var{code}$ requiring $\dom(\mscode') \subseteq \ta$ and $\dom(\mscode) = \ta$ and finally that $\mscode$ is part of $\ms_S$.}
  such that
  \begin{equation}
    \npair{(\mscode',\mscode')} \in H^{\var{code}} \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\_,\gsigrets,\gsigcloss)\label{eq:ftlr:rretd:Hcode}
  \end{equation}
  where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$.
  \dominique{How do we know $\ms_\code'$ contains [b,e] entirely?
    It does seem plausible that it contains the call entirely as well as $a + \offpc$ thanks to the code region's well-formedness.
  }
  That is: $\mscode'$ contains the call we are considering.
  This also entails
  \begin{equation}
    \label{eq:ftlr:code-comp-jud}
    \sigrets',\sigcloss' \vdash_\var{code\_comp} \mscode'
  \end{equation}
  from \ref{eq:ftlr:rretd:Hcode} we also get
\begin{itemize}
\item $\dom(\mscode') \subseteq \ta$

  Otherwise we would have $\dom(\mscode') \# \ta$ which would contradict $\dom(\mscode') \subseteq \dom(\mscode) \subseteq\ta$

@@

    Use the $r=r_{\mscode'}$ as the witness.
    The $\xReadCond{}$ gives us $\pwheap(r) \nequal \codereg{\_,\_,\mscode',\gc}$.
    As it is a pure region, it is also present in the future world we consider.
    We now have to show:
    \begin{enumerate}[label=\alph*)]
    \item for $n'' < n-1$ we have
      \[\npair[n'']{\left(\array{l}\retptrd(\aaddr_\stk,\eaddr_\stk),\\((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)\endarray\right)}
        \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
        \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretd}')
      \]
      First, we already know $\dom(\mscode') \subseteq \ta$ and $\sigrets' \subseteq \gsigrets$.
      Now pick $r_\var{priv\_stk}$ as the witness.
      We immediately get $\dom(\ms_{\stk\_\priv,S}) = \dom(\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}) = [\aaddr_\stk,\eaddr_\stk]$.
      Next, $\decInstr{\mscode'(\aaddr,\aaddr+\calllen-1)} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$ follows from $\callCond{\Phi_S,r_1,r_2,\offpc,\offsigma,\aaddr}$.
      Finally, $\ms_\code(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr}$ with $\sigma' = \sigma_\baddr + \offpc \in \sigrets'$ which follows from $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$ and the fact that the call is there.
    \item $\isLinear{\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}}$ iff
      $\isLinear{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk)}}$\\
      Trivial, both are linear.
    \item
      \[
        \begin{array}{l}
          \forall W'' \future \purePart{W_{R,\rretd}'}, W_o, n'' < n-1,\\
          \quad\npair[n'']{(\vsc_S',\vsc_T')}
          \in  H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
          \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
          \qquad\npair[n'']{\retptrd(\aaddr_\stk,\eaddr_\stk),\vsc_S',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1),\vsc_T'} \in
          \lrexj(W'\oplus W_o))
        \end{array}
      \]
      Trivial as both configurations fails.
    \end{enumerate}

  \item[Case $\rretc$:]
    We have to show
    \[
      \npair[n-1]{\left(\array{l}\sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr +
            \calllen)},\\\sealed{\sigma',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)}\endarray\right)} \in \lrv(W_{R,\rretc}')
    \]
    where $W_{R,\rretc}'$ has the ownership of $W$.
    Just as in the previous case, we know that for some region $r$ there exists $\mscode' \subseteq \mscode$ such that: $\pwheap(r) \nequal \codereg{\sigrets',\_,\mscode',\gc}$ where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$ and $\sigrets' \subseteq \gsigrets$.
    It follows easily from the definition of $H_\sigma^\var{code}$ that
    \begin{equation}
      \label{eq:code-caps-in-h-sigma}
      \npair[n'']{\left(\array{l}\retptrc(\baddr,\eaddr,\aaddr + \calllen),\\((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)\endarray\right)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretc}')
    \end{equation}
    for $n'' < n-1$.
    Both capabilities are non-linear, so
    \[
      \isLinear{\retptrc(\baddr,\eaddr,\aaddr + \calllen)}\text{ iff } \isLinear{((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)}
    \]
    is indeed the case.

    Finally we need to show:
    \[
      \begin{array}{l}
        \forall W'' \future \purePart{W_{R,\rretc}'}, W_o, n'' < n-1,\\
        \quad  \npair[n'']{(\vsc_S',\vsc'_T)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
        \qquad \npair[n'']{\retptrc(\baddr,\eaddr,\aaddr + \calllen),\vsc_S',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset),\vsc_T'} \in \lrexj(W''\oplus W_o))
      \end{array}
    \]

    To this end let $W'' \future \purePart{W_{R,\rretc}'}$ and $W_o$ be given s.t. $W'' \oplus W_o$ is defined.
    Further, let $\npair[n'']{(\vsc_S',\vsc'_T)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o)$ be given and show
    \[
      \npair[n'']{\retptrc(\baddr,\eaddr,\aaddr + \calllen),\vsc_S',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset),\vsc_T'} \in \lrexj(W''\oplus W_o))
    \]

@@

    Based on $H_\sigma^\var{code}$, there are three possible values for $\vsc_S'$ and $\vsc_T'$.
    In the first case, $\vsc_S'$ is a $\retptrc$ and $\vsc_T'$ is a capability with permission $\rx$.
    In this case, $\var{xjumpResult}$ will produce failed configurations which are trivially in the observation relation.
    In the next case, it is required that $\sigma' \in \sigcloss'$, but this
    cannot be the case as $\sigma' \in \sigrets'$ and we have $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$, which implies that $\sigcloss' \mathrel{\#} \sigrets'$.

>>>>

\begin{lemma}[Capability splicing retains safety for normal capabilities]
  \label{lem:splitting-safety-normal}
  If
  \begin{itemize}
  \item $\npair{(c_1,c_1)} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_2,c_2)} \in \lrvg{\trust}(W_2)$
  \item $c_1 = ((\perm,\lin),\baddr,m,\aaddr)$
  \item $c_2 = ((\perm,\lin),m+1,\eaddr,\aaddr)$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $b \le m \le e$
  \item $c_1' = \linCons{c_1}$
  \item $c_2' = \linCons{c_2}$
  \item $W_1\oplus W_2 \oplus W_M$ is defined
  \item $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$
  \end{itemize}
  then there exist $W_1',W_2',W_3'$ such that
  \begin{itemize}
  \item $W_1 \oplus W_2 = W_1' \oplus W_2' \oplus W_3'$
  \item $\npair{(c,c)} \in \lrvg{\trust}(W_3')$
  \item $\npair{(c_1',c_1')} \in \lrvg{\trust}(W_1')$
  \item $\npair{(c_2',c_2')} \in \lrvg{\trust}(W_2')$
  \end{itemize}
\end{lemma}
\begin{proof}
  From $\npair{(c_1,c_1)} \in \lrvg{\trust}(W_1)$ and $\npair{(c_2,c_2)} \in \lrvg{\trust}(W_2)$, it follows that either ($[b,m] \mathrel{\#} \ta$ or $[b,m] \subseteq \ta$) and also either ($[m+1,e] \mathrel{\#} \ta$ or $[m+1,e] \subseteq \ta$).

  Consider first the case where either $[b,m] \subseteq \ta$ or $[m+1,e]\subseteq \ta$.
  Then by definition of $\lrvg{\trust}$, we have that $\lin = \normal$, $\trust = \trusted$ and $\npair{[b,m]} \in \xReadCond{W_1}$ or $\npair{[m+1,e]} \in \xReadCond{W_2}$, respectively.
  It follows by definition of $\xReadCond{}$ and $\codereg{}$ that $[\baddr-1,m+1]$ or $[m,\eaddr+1] \subseteq \ta$, respectively, so that it is impossible that $[m+1,\eaddr]\mathrel{\#} \ta$ or $[\baddr,m] \mathrel{\#} \ta$ respectively.
  In other words, we must have that both $[b,m] \subseteq \ta$ and $[m+1,e]\subseteq \ta$.

  From Lemma~\ref{lem:conds-splicable}, it follows that also $\npair{[\baddr,\eaddr]}\in\xReadCond{W_1\oplus W_2}$ and from Lemma~\ref{lem:non-linear-pure}, it follows that $\npair{[\baddr,\eaddr]}\in\xReadCond{}(\purePart{W_1\oplus W_2})$.
  Finally, we have that $\npair{(c,c)}\in\lrvg{\trust}(\purePart{W_1\oplus W_2})$.
  We can take $W_3' = \purePart{W_1\oplus W_2}$, $W_1' = W_1$ and $W_2' = W_2$ and the remaining proof obligations follow by assumption and by Lemma~\ref{lem:purePart-duplicable} and~\ref{lem:oplus-assoc-comm}.

  Now consider the case that both $[b,m] \mathrel{\#} \ta$ and $[m+1,e]\mathrel{\#} \ta$.
  The results now follow by definition of $\lrv$, using Lemma~\ref{lem:conds-splicable} and~\ref{lem:non-linear-pure}, taking $W_3' = W_1 \oplus W_2$ and $W_1' = \purePart{W_1}$ and $W_2' = \purePart{W_2}$.
\end{proof}

@@

\begin{lemma}
  \label{lem:ftlr-internal-lemma}
  If
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \ta$
    \item $\trust = \untrusted$ and $[b,e] \mathrel{\#} \ta$ and $\npair{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
  \item $\Phi_S(\pcreg) = \Phi_T(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$
  \item $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$
  \item $\memSat{\Phi_S.\mem,\Phi_S.\stk,\Phi_S.\ms_\stk,\Phi_T.\mem}{W_M}$
  \item $W_\pcreg \oplus W_R \oplus W_M$ is defined.
  \item Theorem~\ref{thm:ftlr} holds for all $n' < n$.
  \end{itemize}
  Then
  \[
    \npair{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  In the following we will use the following: $\reg_S = \Phi_S.\reg$, $\reg_T = \Phi_T.\reg$, $\ms_S = \Phi_S.\mem$, $\ms_\stk = \Phi_S.\ms_\stk$, and $\stk = \Phi_S.\stk$.

@@

  In case \ref{case:ftlr:failed}, both executions go to $\failed$.
  In this case, the result follows vacuously by definition of $\lrol$ and $\lror$.
  \\\\
  In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
  steps, so both directions of $\lro$ are trivially satisfied.
  \\\\
  In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to conclude
  \[
    \npair[n-1]{(\Phi_S',\Phi_T')} \in \lro
  \]
  from the following facts:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
    This follows from the corresponding assumption of this lemma and the fact that $\Phi_S \nstep[1]{\gc} \Phi_S'$ and Lemma~\ref{lem:ec-reasonable-antired}, \ref{lem:ec-reasonable-downwards-closed}, and \ref{lem:downwards-closed}.
  \item $\Phi_S'(\pcreg) = \Phi_T'(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$:
    Follows from the definition of $\updPcAddr{}$ and the assumptions of this case.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item $\npair[n-1]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}, the definition of $\lrr$ and the fact that integers are always in $\lrvg{\trust}$ by definition.
  \item $\memSat[n-1]{\Phi_S.\mem,\Phi_S.\ms_\stk,\Phi_S.\stk,\Phi_T.\mem}{W_M}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item Theorem~\ref{thm:ftlr} holds for all $n'' < n-1$:
    follows from the corresponding assumption of this lemma, since $n - 1 < n$.
  \end{itemize}

@@

  It remains to show \ref{case:ftlr:scall:world}-\ref{case:ftlr:scall:mem}, but first we note that we can deduce the following: From the assumption $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ we get $r \in \addressable{\normal, \pwheap}$ and $\mscode$ such that $\dom(\mscode) \supseteq [\baddr,\eaddr]$ and $\pwheap(r) \nequal \codereg{\sigrets',\_,\mscode,\gc}$.
  Further by $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, we know that
  \begin{equation}
    \npair{(\mscode\uplus\mspad,\mscode\uplus\mspad)} \in H^{\var{code}} \; \sigrets' \; \sigcloss' \; \mscode \; (\ta,\_,\gsigrets,\gsigcloss)~ W_r\label{eq:ftlr:rretd:Hcode}
  \end{equation}
  where $\sigma' \in \sigrets'$ and $\dom(\mscode) \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode)$ and $W = W_r \oplus \_$.
  That is: $\mscode$ contains the call we are considering.
  This also entails
  \begin{equation}
    \label{eq:ftlr:code-comp-jud}
    \sigrets',\sigcloss' \vdash_\var{code\_comp} \mscode
  \end{equation}
  from \ref{eq:ftlr:rretd:Hcode} we also get
\begin{itemize}
\item $\dom(\mscode\uplus\mspad) \subseteq \ta$

  Otherwise we would have $\dom(\mscode\uplus\mspad) \# \ta$ which would contradict $\ta\supseteq [b,e] \subseteq\dom(\mscode\uplus\mspad)$

@@

    Use the $r=r_{\mscode}$ as the witness.
    The $\xReadCond{}$ gives us $\pwheap(r) \nequal \codereg{\_,\_,\mscode,\gc}$.
    As it is a pure region, it is also present in the future world we consider.
    We now have to show:
    \begin{enumerate}[label=\alph*)]
    \item for $n'' < n-1$ we have
      \[\npair[n'']{\left(\array{l}\retptrd(\aaddr_\stk,\eaddr_\stk),\\((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)\endarray\right)}
        \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
        \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretd}')
      \]
      First, we already know $\dom(\mscode) \subseteq \ta$ and $\sigrets' \subseteq \gsigrets$.
      Now pick $r_\var{priv\_stk}$ as the witness.
      We immediately get $\dom(\ms_{\stk\_\priv,S}) = \dom(\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}) = [\aaddr_\stk,\eaddr_\stk]$.
      Next, $\decInstr{\mscode'(\aaddr,\aaddr+\calllen-1)} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$ follows from $\callCond{\Phi_S,r_1,r_2,\offpc,\offsigma,\aaddr}$.
      Finally, $\ms_\code(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr}$ with $\sigma' = \sigma_\baddr + \offpc \in \sigrets'$ which follows from $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode$ and the fact that the call is there.
    \item $\isLinear{\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}}$ iff
      $\isLinear{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk)}}$\\
      Trivial, both are linear.
    \item
      \[
        \begin{array}{l}
          \forall W'' \future \purePart{W_{R,\rretd}'}, W_o, n'' < n-1,\\
          \quad\npair[n'']{(\vsc_S',\vsc_T')}
          \in  H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
          \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
          \qquad\npair[n'']{\retptrd(\aaddr_\stk,\eaddr_\stk),\vsc_S',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1),\vsc_T'} \in
          \lrexj(W'\oplus W_o))
        \end{array}
      \]
      Trivial as both configurations fails.
    \end{enumerate}

  \item[Case $\rretc$:]
    We have to show
    \[
      \npair[n-1]{\left(\array{l}\sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr +
            \calllen)},\\\sealed{\sigma',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)}\endarray\right)} \in \lrv(W_{R,\rretc}')
    \]
    where $W_{R,\rretc}'$ has the ownership of $W$.
    Just as in the previous case, we know that for some region $r$ there exists an $\mscode$ such that: $\pwheap(r) \nequal \codereg{\sigrets',\_,\mscode,\gc}$ where $\sigma' \in \sigrets'$ and $\dom(\mscode) \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode)$ and $\sigrets' \subseteq \gsigrets$.
    It follows easily from the definition of $H_\sigma^\var{code}$ that
    \begin{equation}
      \label{eq:code-caps-in-h-sigma}
      \npair[n'']{\left(\array{l}\retptrc(\baddr,\eaddr,\aaddr + \calllen),\\((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)\endarray\right)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretc}')
    \end{equation}
    for $n'' < n-1$.
    Both capabilities are non-linear, so
    \[
      \isLinear{\retptrc(\baddr,\eaddr,\aaddr + \calllen)}\text{ iff } \isLinear{((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)}
    \]
    is indeed the case.

    Finally we need to show:
    \[
      \begin{array}{l}
        \forall W'' \future \purePart{W_{R,\rretc}'}, W_o, n'' < n-1,\\
        \quad  \npair[n'']{(\vsc_S',\vsc'_T)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
        \qquad \npair[n'']{\retptrc(\baddr,\eaddr,\aaddr + \calllen),\vsc_S',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset),\vsc_T'} \in \lrexj(W''\oplus W_o))
      \end{array}
    \]

    To this end let $W'' \future \purePart{W_{R,\rretc}'}$ and $W_o$ be given s.t. $W'' \oplus W_o$ is defined.
    Further, let $\npair[n'']{(\vsc_S',\vsc'_T)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o)$ be given and show
    \[
      \npair[n'']{\retptrc(\baddr,\eaddr,\aaddr + \calllen),\vsc_S',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset),\vsc_T'} \in \lrexj(W''\oplus W_o))
    \]

@@

    Based on $H_\sigma^\var{code}$, there are three possible values for $\vsc_S'$ and $\vsc_T'$.
    In the first case, $\vsc_S'$ is a $\retptrc$ and $\vsc_T'$ is a capability with permission $\rx$.
    In this case, $\var{xjumpResult}$ will produce failed configurations which are trivially in the observation relation.
    In the next case, it is required that $\sigma' \in \sigcloss'$, but this
    cannot be the case as $\sigma' \in \sigrets'$ and we have $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode$, which implies that $\sigcloss' \mathrel{\#} \sigrets'$.
